%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[left=0.5 in,top=0.5 in,right=0.5 in,bottom=0.5]{geometry} % Document margins
\usepackage{ragged2e}
\usepackage[spanish]{babel}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\hypersetup{
    colorlinks = true,
    linkbordercolor = [rgb]{1,1,1},
    linkcolor = [rgb]{0,0,0.5},
    anchorcolor = [rgb]{0,0,0.5},
    citecolor = [rgb]{0,0,0.5},
    filecolor = [rgb]{0,0,0.5},
    urlcolor = [rgb]{0,0,0.5}}

\name{Iván Vallés Pérez} % Your name




\begin{document}

\noindent

\printname
\vspace{5pt}

\begin{minipage}[t]{.345\textwidth}
	\raggedright


Ph.D. at University of Valencia and Sr. Applied Scientist at Amazon AGI, with  10 years of industry experience.
\textbf{Looking for a Research Scientist position}.

\end{minipage}\hspace{.05\textwidth}
\begin{minipage}[t]{.29\textwidth}
	\raggedright
	{\textbf{phone}: +44 (0) 7899 865 681 \\
	\textbf{mail}: \href{mailto:ivanvallesperez@gmail.com}{ivanvallesperez@gmail.com}\\
	\textbf{chime \& skype}: @ivallesp \\
	\textbf{addr.}: Cambridge (UK)
}
\end{minipage}\hspace{.03\textwidth}
\begin{minipage}[t]{.29\textwidth}
	\raggedright
	{ \textbf{gh}: \href{https://www.github.com/ivallesp}{github.com/ivallesp}  \\
	  \textbf{kaggle}: \href{https://www.kaggle.com/ivallesp}{kaggle.com/ivallesp}  \\
	  \textbf{so}: \href{https://stackoverflow.com/users/3742686/ivallesp}{stackoverflow.com/u/3742686} \\
	  \textbf{lkdin}: \href{https://www.linkedin.com/in/ivallesp}{linkedin.com/in/ivallesp}
	}
\end{minipage}


%------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------
\vspace{5pt}

\begin{rSection}{Work Experience} \itemsep -1pt
	
\begin{rSubsection}{05.2023 - Present $|$ Senior Applied Scientist at Amzon AGI  $|$  \textnormal{Cambridge, UK}}{}{}

	\vspace{-3pt}
	
	\item Tech lead of global multimodal LLM design and implementation.
	\item Tech lead of the Alexa low-latency  speech generation LLM. Leading the research and supporting productionization.
	\item Lead team of up to 6 scientists and various cross-organization collaborations.
	
\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{09.2020 - 05.2023 $|$ Applied Scientist at Amzon AGI  $|$  \textnormal{Cambridge, UK}}{}{}
	
	\vspace{-3pt}
	
	\item Leading research on probabilistic modelling of found speech data.
	\item Worked with normalizing flows, GANs, diffusion models, LLMs, and other deep learning generative models.

\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{04.2019 - 09.2020 $|$ Senior Data Scientist at Amazon Supply Chain Science  $|$  \textnormal{Luxembourg, Luxembourg}}{}{}

	\vspace{-3pt}

	\item First team member, in charge of bringing the (deep) ML expertise to EU Supply Chain teams.
	\item Designed a Machine learning model to  forecast the daily inbound demand at warehouse level for all EU.
	\item Built a Deep Reinforcement Learning algorithm for improving speed through inventory proactive transfers.
	
\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{06.2013 - Present $|$ AI Researcher at Intelligent Data Analysis Laboratory (UV) $|$ \textnormal{Valencia, Spain}\hspace{-10pt}}{}{}

	\vspace{-3pt}

	\item Involved in several research lines related to low-resource Deep Learning algorithms.

\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{06.2016 - 02.2019 $|$ Senior Data Scientist at McKinsey \& Company  $|$ \textnormal{Madrid, Spain}}{}{}

    \vspace{-3pt}

    \item Developed machine learning solutions for more than 10 clients around the globe belonging to 5 different industries.
    \item Developed 5 customer-ready applications using state-of-the-art Deep Learning techniques.
    \item Lead teams up to 10 data scientists and data engineers.
\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{11.2014 - 06.2016 $|$ Lead Data Scientist at Quarizmi AdTech  $|$  \textnormal{Valencia, Spain}}{}{}

    \vspace{-3pt}

    \item Used Machine Learning and NLP techniques to generate and maintain digital marketing campaigns in Google Adwords.
\end{rSubsection}

	\vspace{-3pt}

\begin{rSubsection}{05.2014 - 11.2014 $|$ Data Scientist at Psychology department of University of Valencia  $|$  \textnormal{Valencia, Spain}}{}{}

    \vspace{-3pt}

    \item Analysis and machine learning modeling of data coming from clinical psychology studies.

\end{rSubsection}


\end{rSection}

\vspace{5pt}
%------------------------------
%	EDUCATION SECTION
%------------------------------
\begin{rSection}{Education}
{\textbf{2018-2023 $|$ Ph.D. in low resource Deep Learning}  $|$  University of Valencia, Spain}
\\
{\textbf{2016-2018 $|$ M.Sc. Languages and Computer Science Systems (NLP)}  $|$  UNED, Spain}
\\
{\textbf{2009-2013 $|$ B.Eng. Electronics of Telecommunications}  $|$ University of Valencia, Spain}\\
{... +30 machine-learning related  courses and specializations from Coursera, EdX, Udacity, etc.}
\end{rSection}

%\begin{rSection}{Further Education}
%{\textbf{2018 $|$ Deep Reinforcement Learning Nanodegree}  $|$  Udacity}\\
%{\textbf{2018 $|$ Practical Reinforcement Learning}  $|$  National Research University Higher School of Economics, Coursera} \\
%{\textbf{2017 $|$ Deep Learning Specialization}  $|$  Andrew Ng, Coursera}\\
%{\textbf{2017 $|$ Neural Networks and Machine Learning}  $|$  Geoffrey Hinton, Coursera}\\
%\end{rSection}



%------------------------------
%	PROJECTS SECTION
%------------------------------
\vspace{5pt}

\begin{rSection}{PROJECTS AND RELEVANT ACHIEVEMENTS}


\begin{rSubsection}{02.2023 $|$ Contributions \& applications to low resource deep learning    $|$  \textnormal{Ph.D. thesis  $|$  Unanimous cum laude}}{}{}{}  
	\vspace{-3pt}
	\item Scientific contributions to deep learning with limited resources. Link: 
	\href{https://roderic.uv.es/handle/10550/85791}{ir.uv.es/ivape3/phd}
	\item Conducted on partial time, while working full-time.
	
\end{rSubsection}
\vspace{-6pt}
\begin{rSubsection}{06.2018 $|$ Generative Adversarial Networks for text generation  $|$  \textnormal{M.Sc. thesis  $|$  Mark: 4/4}}{}{}{}  %June 2016 - November 2016

\vspace{-3pt}

\item Language Modeling using GANs. Link: \href{https://www.uv.es/ivape3/memoria_tfm.pdf}{ir.uv.es/ivape3/tfm}

\end{rSubsection}

\vspace{-6pt}

\begin{rSubsection}{11.2012 $|$ Application of Genetic Algorithms to Extreme Learning Machine  $|$  \textnormal{B.Eng. thesis  $|$  Mark: 3.7/4}}
{}{}{}

\vspace{-3pt}

\item Alternative  to backpropagation for training shallow neural networks. Link: \href{https://www.uv.es/ivape3/memoria_pfc.pdf}{ir.uv.es/ivape3/pfc}

\end{rSubsection}

\vspace{-6pt}

\begin{rSubsection}{Open Source Contributions to machine learning related projects}
	{}{}{}

	\vspace{-3pt}

	\item Contributed open source Python libraries in GitHub: \textit{Tensorflow}, \textit{Scikit-Learn}, \textit{Pandas}, \textit{XGboost}, \textit{SomPy}, ...
	\item Developed  \textit{Somnia} library implementing Self-Organising Maps in Python. Available in my GitHub.
\end{rSubsection}

\vspace{-6pt}

\textbf{Kaggle competitions:} BNP: 22nd/2947 $|$ Santander recommender: 22nd/1787 $|$ SpringLeaf: 76th/2225.


%\textbf{Attendance at research conferences:} NeurIPS 2016, 2017, 2018, 2022, ESANN 2021, ECAI 2023.
\end{rSection}

%------------------------------
%	SKILLS SECTION
%------------------------------

\vspace{5pt}

\begin{rSection}{Skills} \itemsep -3pt
{\textbf{Coding}: Python (Pytorch, Tensorflow, MxNet, Stable Baselines and Ray+RLLib), Rust, Bash, Godot, R, Matlab, \LaTeX, C++, Git \& Mercurial, Docker, etc}. \\
{\textbf{Data}: SQL, Apache Spark, sed  \& awk}.\\
{\textbf{Cloud \& distributed:} AWS, Google Cloud, Distributed computation, Microsoft DeepSpeed}. \\
{\textbf{Languages:} native in Spanish and Catalan. Professional proficiency in English.}
\end{rSection}

\begin{flushright}
	\small{\textit{Referees, references, recommendation letters and additional information will be provided upon request.}}
\end{flushright}
%------------------------------
%	JOURNAL PAPERS SECTION
%------------------------------
\newpage
\begin{rSection}{Peer-reviewed publications}
{\textbf{{2023} $|$ SCRAPS: Speech Contrastive Representations of Acoustic and Phonetic Spaces }, \textit{European Conference on Artificial Intelligence},I. Vallés-Pérez, G. Beringer, P. Bilinski, G. Cook, R. Barra-Chicote}\\
{\textbf{{2023} $|$ Empirical study of the modulus as activation function in computer vision applications}, \textit{Engineering Applications of AI}, I. Vallés-Pérez, E. Soria-Olivas, M. Martínez-Sober, A. J. Serrano-López, J. Vila-Francés, J. Gómez-Sanchís}\\
{\textbf{{2022} $|$ Stutter-TTS: Controlled synthesis and improved recognition of stuttered speech }, \textit{Neural Information Processing Systems}, X. Zhang, I. Vallés-Pérez, A. Stolcke, C. Yu, J. Droppo, O. Shonibare, R. Barra-Chicote, V. Ravichandran}\\
%{\textbf{{2022} (submitted) $|$ Distilling the Knowledge of Pre-trained Models}, \textit{Journal of Computational Science}, I. Vallés-Pérez, E. Soria-Olivas, J. Gómez-Sanchís, M. Martínez-Sober, F. Mateo, J. Vila-Francés }\\
{\textbf{{2022} $|$ Approaching sales forecasting using recurrent neural networks and transformers}, \textit{Expert Systems with Applications}, I. Vallés-Pérez, E. Soria-Olivas, M. Martínez-Sober, A. J. Serrano-López, J. Gómez-Sanchís, F. Mateo}\\
{\textbf{{2021} $|$ End-to-end Keyword Spotting using Xception-1d}, \textit{European Symposium of Artificial Neural Networks}, I. Vallés-Pérez, F. Mateo, J. Vila-Francés, A. J. Serrano-López, E. Soria-Olivas}\\
{\textbf{{2021} $|$ Improving multi-speaker TTS prosody variance with a residual encoder and normalizing flows}, \textit{InterSpeech}, I. Vallés-Pérez, J. Roth, G. Beringer, R. Barra-Chicote, J. Droppo}\\
{\textbf{{2014} $|$ Visual Data Mining With Self-Organizing Maps for ``Self-monitoring'' Data Analysis}, \textit{Sociological Methods \& Research}, E. Oliver-Gasch, I. Vallés-Pérez, R.M. Baños-Rivera, A.J. Cebolla-Martí, C. Botella-Arbona, E. Soria-Olivas}\\
{\textbf{{2014} $|$ Self-Organizing Maps (SOM) in the analysis of EMAs in a treatment for childhood obesity treatment}, \textit{International Society for Research on Internet Intervention (ISRII)}, R. Baños, E. Oliver, A.J. Cebolla, I. Vallés, E. Soria, C. Botella}
\end{rSection}

\vspace{5pt}

\begin{rSection}{Other publications}
{\textbf{{2024} $|$ Enhancing the Stability of LLM-based Speech Generation Systems through Self-Supervised Representations }, \textit{arXiv preprint},A. Martín-Cortinas, D. Sáez-Trigueros, I. Vallés-Pérez, B. Tura-Vecino, P. Biliński, M. Lajszczak, G. Beringer, R. Barra-Chicote, J. Lorenzo-Trueba}
\end{rSection}

\vspace{\fill}

\end{document}



